---
title: "Car_viz_h"
author: "Carolyn Wright"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("knitr","ggplot2", "tidyverse", "esquisse")
options(warn = -1)
```

```{r}
# call built-in data mtcars.
data(mtcars)

```
mtcars {datasets}

<header>Motor Trend Car Road Tests</header>
 + Description
  + The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

<header>Usage</header>
 + mtcars-->
 
<header>Format</header>
 + A data frame with 32 observations on 11 (numeric) variables.

   + [, 1]	mpg	Miles/(US) gallon

   + [, 2]	cyl	Number of cylinders

   + [, 3]	disp	Displacement (cu.in.)

   + [, 4]	hp	Gross horsepower

   + [, 5]	drat	Rear axle ratio

   + [, 6]	wt	Weight (1000 lbs)

   + [, 7]	qsec	1/4 mile time

   + [, 8]	vs	Engine (0 = V-shaped, 1 = straight)

   + [, 9]	am	Transmission (0 = automatic, 1 = manual)

   + [,10]	gear	Number of forward gears

   + [,11]	carb	Number of carburetors

<header>Note</header>
 + Henderson and Velleman (1981) comment in a footnote to Table 1: Hocking [original transcriber]s noncrucial coding of the Mazdas rotary engine as a straight six-cylinder engine and the Porsches flat engine as a V engine, as well as the inclusion of the diesel Mercedes 240D, have been retained to enable direct comparisons to be made with previous analyses.

<header>Source</header>
 + Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.
 
```{r}
# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]

# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]

# read the R file hand_functions.R so that it can be used
# note I have changed echo to false so that the source code will not be displayed
source(file = "hand_functions.R", echo = FALSE)

# Now use the function from hand_functions.R
sp_out <- sum_special(mtcars_mpg2)
```
 
