---
title: "Car_viz_h"
author: "Carolyn Wright"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("knitr","ggplot2", "tidyverse", "esquisse")
options(warn = -1)
```

```{r}
# call built-in data mtcars.
data(mtcars)

```
<header><b> Documentation on mtcars dataset</header></b>

<header>Motor Trend Car Road Tests</header>
 + Description:
   + The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

<header>Usage</header>
 + mtcars-->
 
<header>Format</header>
 + A data frame with 32 observations on 11 (numeric) variables.

   + [, 1]	mpg	Miles/(US) gallon

   + [, 2]	cyl	Number of cylinders

   + [, 3]	disp	Displacement (cu.in.)

   + [, 4]	hp	Gross horsepower

   + [, 5]	drat	Rear axle ratio

   + [, 6]	wt	Weight (1000 lbs)

   + [, 7]	qsec	1/4 mile time

   + [, 8]	vs	Engine (0 = V-shaped, 1 = straight)

   + [, 9]	am	Transmission (0 = automatic, 1 = manual)

   + [,10]	gear	Number of forward gears

   + [,11]	carb	Number of carburetors

<header>Note</header>
 + Henderson and Velleman (1981) comment in a footnote to Table 1: Hocking [original transcriber]s noncrucial coding of the Mazdas rotary engine as a straight six-cylinder engine and the Porsches flat engine as a V engine, as well as the inclusion of the diesel Mercedes 240D, have been retained to enable direct comparisons to be made with previous analyses.

<header>Source</header>
 + Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.
 
```{r}
# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]

# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]

# read the R file hand_functions.R so that it can be used
# note I have changed echo to false so that the source code will not be displayed
source(file = "hand_functions.R", echo = FALSE)

# Now use the function from hand_functions.R
sp_out <- sum_special(mtcars_mpg2)

```
<br>

<header><b>Look at some results from 'sum_special' function</header></b>

 + Means:
```{r}
#call the sp_means that is a list of means included in sp_out
sp_out$sp_means

```
 
 + Variance:
```{r}
#call the sp_var that is a list of variances included in sp_out
sp_out$sp_var

```
<br>

<b><header> Investigate the esquisse package</header></b>

```{r}
#esquisser(data = mtcars, viewer = "browser")

#include code that is created through the esquisse package
ggplot(mtcars) +
 aes(x = wt, y = mpg, size = hp) +
 geom_point(shape = "diamond filled", colour = "#458ED2") +
 labs(x = "Weight(1000 lbs)", y = "Miles/(US) gallon", 
      title = "Motor Trend Car Road Tests", size = "Gross horsepower") +
 theme_bw() +
 theme(legend.position = "top") +
 facet_wrap(vars(cyl), ncol = 1L)
```

```{r}
# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?
ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")

```
<header> Discussion of above boxplot</header>
 + The above boxplot cannot be created using esquisse() due to the fact that the variable 'cyl' is not defined as a factor in the raw data. Below is the code for changing 'cyl' into a factor variable in the raw data.
 
```{r}
#convert 'cyl' into a factor in the raw data
mtcars$cyl <-as.factor(mtcars$cyl)

#check variable type--> output should be "TRUE" if the conversion worked properly
is.factor(mtcars$cyl)

```
 
